Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2020-12-29 RR_manuscript/Draft_RR.Rmd
use package cleveref
update sample size justification

documentclass     : "apa6"
classoption       : "man"
output:
  papaja::apa6_pdf:
    number_sections: true
---

@@

<!-- sample size info from Ecology RR -->
<!-- SC: rephrased and expanded -->
To identify the minimal sample size, we followed the method in [ECO RR].
The aim of the meta-analysis is to obtain an estimate of heterogeneity ($\tau^2$) of the effect sizes reported by the analysis teams.
Ideally, the 95% credible interval of $\tau^2$ should not include 0 (i.e. we want to be able to exclude the hypothesis that there is no heterogeneity, or, to put it differently, we want to ensure we obtain a *t*-statistic that would correspond to a *p*-value smaller than 0.05).
Assuming that the underlying distribution of effect sizes is normal (Knight 2000), the standard error of $\tau^2$ can be calculated with the formula:

@@

Plugging $SE(\tau^2)$ into the formula of the *t*-statistics shows that *t* will be the same regardless of $\tau^2$:

@@

In other words, the minimum sample size $n$ needed to exclude 0 from the 95% CI of $\tau^2$ is invariant regardless of the estimate of heterogeneity $\tau^2$.
When $n = 12$ then $t_{12-1} = t_{11} = 2.3452$ and $p = 0.0388$.
A minimal sample size of effect sizes of 12 would thus be sufficient to ensure enough statistical power.

@@

### Meta-analytical estimation

>>>>

documentclass     : "apa6"
classoption       : "man"
output:
  papaja::apa6_pdf:
    number_sections: true
header-includes:
  - \usepackage{cleveref}
---

@@

<!-- sample size info from Ecology RR -->
<!-- SC: rephrased and expanded -->
<!-- TODO: include citation to ECO RR -->
To identify the minimal sample size, we followed the method in [ECO RR].
The aim of the meta-analysis is to obtain an estimate of heterogeneity of the effect sizes reported by the analysis teams ($\tau^2$, i.e. the variance $\sigma^2_{\alpha_{\text{team}}}$, see \Cref{s:meta-est}).
Ideally, the 95% credible interval (CrI) of $\tau^2$ should not include 0 (i.e. the probability $p$ that the 95% CrI contains 0 should be less than 0.05).
The probability $p$ that a CrI interval does not include 0 is obtained via the *t*-statistics:

$$t = \frac{\tau^2}{SE(\tau^2)}$$

Assuming that the underlying distribution of effect sizes is normal (Knight 2000), the standard error of $\tau^2$ can be calculated with the formula:

@@

where $n$ is the sample size.
Since we know $p$ and $\tau^2$, we can calculate $n$ such that $p < 0.05$.
Plugging $SE(\tau^2)$ into the formula of the *t*-statistics shows that, when $n$ is fixed, *t* (and hence $p$) will be the same regardless of $\tau^2$:

@@

In other words, the minimum sample size $n$ needed to exclude 0 from the 95% CrI of $\tau^2$ is invariant regardless of the estimate of heterogeneity $\tau^2$.
When $n = 12$ then $t_{(12-1)} = t_{(11)} = 2.3452$ and $p = 0.0388$, which is below the 0.05 threshold, as required.
In sum, a minimal sample of 12 effect sizes (i.e. of 12 analysis teams) would thus be sufficient to exclude 0 from the 95% CrI of $\tau^2$.

@@

### Meta-analytical estimation {#s:meta-est}

### 2020-12-29 RR_manuscript/Draft_RR.tex
update sample size justification

\linenumbers
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

To identify the minimal sample size, we followed the method in {[}ECO RR{]}.
The aim of the meta-analysis is to obtain an estimate of heterogeneity (\(\tau^2\)) of the effect sizes reported by the analysis teams.
Ideally, the 95\% credible interval of \(\tau^2\) should not include 0 (i.e.~we want to be able to exclude the hypothesis that there is no heterogeneity, or, to put it differently, we want to ensure we obtain a \emph{t}-statistic that would correspond to a \emph{p}-value smaller than 0.05).
Assuming that the underlying distribution of effect sizes is normal (Knight 2000), the standard error of \(\tau^2\) can be calculated with the formula:

@@

Plugging \(SE(\tau^2)\) into the formula of the \emph{t}-statistics shows that \emph{t} will be the same regardless of \(\tau^2\):

@@

In other words, the minimum sample size \(n\) needed to exclude 0 from the 95\% CI of \(\tau^2\) is invariant regardless of the estimate of heterogeneity \(\tau^2\).
When \(n = 12\) then \(t_{12-1} = t_{11} = 2.3452\) and \(p = 0.0388\).
A minimal sample size of effect sizes of 12 would thus be sufficient to ensure enough statistical power.

@@

\hypertarget{meta-analytical-estimation}{%
\subsubsection{Meta-analytical estimation}\label{meta-analytical-estimation}}

>>>>

\linenumbers
\usepackage{csquotes}
\usepackage{cleveref}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

To identify the minimal sample size, we followed the method in {[}ECO RR{]}.
The aim of the meta-analysis is to obtain an estimate of heterogeneity of the effect sizes reported by the analysis teams (\(\tau^2\), i.e.~the variance \(\sigma^2_{\alpha_{\text{team}}}\), see \Cref{s:meta-est}).
Ideally, the 95\% credible interval (CrI) of \(\tau^2\) should not include 0 (i.e.~the probability \(p\) that the 95\% CrI contains 0 should be less than 0.05).
The probability \(p\) that a CrI interval does not include 0 is obtained via the \emph{t}-statistics:

\[t = \frac{\tau^2}{SE(\tau^2)}\]

Assuming that the underlying distribution of effect sizes is normal (Knight 2000), the standard error of \(\tau^2\) can be calculated with the formula:

@@

where \(n\) is the sample size.
Since we know \(p\) and \(\tau^2\), we can calculate \(n\) such that \(p < 0.05\).
Plugging \(SE(\tau^2)\) into the formula of the \emph{t}-statistics shows that, when \(n\) is fixed, \emph{t} (and hence \(p\)) will be the same regardless of \(\tau^2\):

@@

In other words, the minimum sample size \(n\) needed to exclude 0 from the 95\% CrI of \(\tau^2\) is invariant regardless of the estimate of heterogeneity \(\tau^2\).
When \(n = 12\) then \(t_{(12-1)} = t_{(11)} = 2.3452\) and \(p = 0.0388\), which is below the 0.05 threshold, as required.
In sum, a minimal sample of 12 effect sizes (i.e.~of 12 analysis teams) would thus be sufficient to exclude 0 from the 95\% CrI of \(\tau^2\).

@@

\hypertarget{s:meta-est}{%
\subsubsection{Meta-analytical estimation}\label{s:meta-est}}
